### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@bcbe5051cbe2512efc17e7645574e9bd042b9fa8 🚀
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@96da5ab50d0162ebdf6d6a957760c7b868229a6a 🚀

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily The coevolutionary mosaic of betacoronavirus
emergence risk}
\vskip 5em

@@

\hypertarget{human-occupancy-drives-different-levels-of-effective-risk-globally}{%
\subsection{Human occupancy drives different levels of effective risk
globally}\label{human-occupancy-drives-different-levels-of-effective-risk-globally}}

Based on the previous result, we extracted the risk component from the
composite map (see Methods), to provide a single measure of risk varying
between 0 and 1. This measure is presented in fig.~\ref{fig:risk}. As
this map represents the potential risk, it must be weighed by the
potential for contacts with humans. As a proxy for this measure, we used
the proportion of build/urban land from the EarthEnv dataset: this is a
reasonable proxy for the density of humans per unit area, which
increases the probability of pathogen spread more
widely.\textsuperscript{20} Since human activity is required to amplify
the frequency of virus encounters and thus create areas of viral
amplification, mapping the potential risk against measures of land use
is required to generate a more actionable assessment of risk. This map
is presented in fig.~\ref{fig:compound}. Most of South America and
Europe are at comparatively lower risk, as although densely populated,
settlements tend to be in areas with lower potential risk. Regions like
Malaysia and the North coast of Australia have a high risk component,
but should represent a relatively lower effective risk due to low human
density. However, this mapping reveals that South-East Asia, the Indian
subcontinent, and parts of sub-Saharan Africa, are at high risk due to
the overlap between built areas and bat communities representing more
opportunities for cross-species transmission of betacoronaviruses. In
looking for the origins of SARS in China,\textsuperscript{21} present
serological evidence that strongest human-animal contact results in
higher risk of virus exposure, regardless of the animal species, but
that different types of contact had different impacts. Ideally,
finer-grained information about human activity (rather than human
presence through anthropisation) could allow to partition this risk
further, alebit at the cost of more hypotheses required to estimate the
amount of risk represented by each activity. Our map of purported high
risk/diversitifcation potential (Madagascar, South-America) overlay with
sampling gaps for \emph{Betacoronavirus},\textsuperscript{17} stressing
the need for spatially targeted monitoring and discovery.

>>>>

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily The coevolutionary mosaic of bat
betacoronavirus emergence risk}
\vskip 5em

@@

\hypertarget{human-landscapes-filter-the-geography-of-emergence-risk}{%
\subsection{Human landscapes filter the geography of emergence
risk}\label{human-landscapes-filter-the-geography-of-emergence-risk}}

The relationship between the underlying pathogen pool and emergence risk
is mediated by human-wildlife contact and the risk that spillovers
become epidemics. As a proxy for both, we finally overlaid the risk
component from the composite map (see above) with the proportion of
built land, as a proxy for a mix of habitat disturbance, potential for
bat synanthropy, and human population density and
connectivity\textsuperscript{1,20} (add: Muylaert 2022 Proc B; Hassell
2017 TREE) (fig.~\ref{fig:compound}).

Most of South America and Europe are at comparatively lower risk, as
although densely populated, settlements tend to be in areas with lower
potential risk. Regions like Malaysia and the North coast of Australia
have a high risk component, but should represent a relatively lower
effective risk due to low human density. However, this mapping reveals
that South-East Asia, the Indian subcontinent, and parts of sub-Saharan
Africa, are at high risk due to the overlap between built areas and bat
communities representing more opportunities for cross-species
transmission of betacoronaviruses. In looking for the origins of SARS in
China,\textsuperscript{21} present serological evidence that strongest
human-animal contact results in higher risk of virus exposure,
regardless of the animal species, but that different types of contact
had different impacts. Ideally, finer-grained information about human
activity (rather than human presence through anthropisation) could allow
to partition this risk further, alebit at the cost of more hypotheses
required to estimate the amount of risk represented by each activity.
Our map of purported high risk/diversitifcation potential (Madagascar,
South-America) overlay with sampling gaps for
\emph{Betacoronavirus},\textsuperscript{17} stressing the need for
spatially targeted monitoring and discovery.
